An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2017-02-22 icml2017/paper.tex
Adding figure drafts to where they would go in the paper.
I'm still using ICML format because UAI doesn't have their format out yet.

% Daniel: moving this here so figures don't overflow to next pages. We can tune
% the positioning if needed.
\begin{figure*}[t]
	\centering
	\includegraphics[width=0.9\linewidth]{logistic_regression_ll_acc_results.png}
	\caption{
    Logistic regression performance (accuracy/log likelihood) based on
    cumulative data usage.
    }
	\label{fig:logistic_performance}
\end{figure*}
\begin{figure*}[t]
	\centering
	\includegraphics[width=0.9\linewidth]{logistic_regression_histograms_results.png}
	\caption{
    Counts of minibatch sizes in the logistic regression experiment (analogous
    to Figure~\ref{fig:gauss_mix_2}).
    }
	\label{fig:logistic_minibatch}
\end{figure*}

>>>>

% Daniel: moving this here so figures don't overflow to next pages. We can tune
% the positioning if needed.
\begin{figure*}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{logistic_regression_error_regions.png}
	\caption{
    TODO
    }
	\label{fig:logistic_performance}
\end{figure*}

\begin{figure*}[t]
	\centering
    \includegraphics[width=0.75\linewidth]{logistic_regression_histograms_mnist.png}
	\caption{
    Minibatch sizes used for one representative trial in
    Section~\ref{ssec:logistic} using MNIST-13k (analogous to
    Figure~\ref{fig:gauss_mix_2}).
    }
	\label{fig:logistic_histograms_mnist}
\end{figure*}

\begin{figure*}[t]
	\centering
    \includegraphics[width=0.75\linewidth]{logistic_regression_histograms_mnist8m.png}
	\caption{
    Minibatch sizes used for one representative trial in
    Section~\ref{ssec:logistic} using MNIST8M-100k (similar to
    Figure~\ref{fig:logistic_histograms_mnist}).
    }
	\label{fig:logistic_histograms_mnist8m}
\end{figure*}

\begin{table}[t]
\caption{Log. Regression Average Minibatch Size (10 Trials)}
\label{tab:logistic}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{l l l l}
\hline
\abovespace\belowspace
Method/Data & MNIST-13k & MNIST8M-100k  \\
\hline
\abovespace
Our Method & $129.8\pm 3.4$ & \textbf{TODO} \\
AustereMH  & \textbf{TODO} & \textbf{TODO} \\
\belowspace
MHSubLhd   & $10752.8\pm 92.9$ & \textbf{TODO} \\
\hline
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

\textbf{Daniel: TODO this section is badly out of date but I will re-write it
and it should be much better than what we had earlier. Also, define a trial
since I say it in the table and figures. Finally, define AustereMH and MHSubLhd,
and come up with a name for our method.}
